A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-13 paper.tex
Revert "Ejemplo"
This reverts commit 9a6452255f89a5e01a483b19ee70778ccfc445ba.
back

\begin{abstract}
The concepts of intuitionistic membership, and intuitionistic center of
area are proposed in this work, in order to propose a novel method for
implementing an intuitionistic fuzzy inference system. The proposed
method was implemented and compared against type-1 fuzzy inference
systems and interval type-3 fuzzy inference systems, with uncertain
means and uncertain standard deviations, by using the
Mackey-Glass time series benchmark. A genetic algorithm was used to
optimize the parameters of each of the methods being compared, and the
results show that the intuitionistic fuzzy inference system performs
better than the other methods.
\end{abstract}

>>>>

\begin{abstract}
The concepts of intuitionistic membership, and intuitionistic center of
area are proposed in this work, in order to propose a novel method for
implementing an intuitionistic fuzzy inference system. The proposed
method was implemented and compared against type-1 fuzzy inference
systems and interval Type-2 fuzzy inference systems, with uncertain
means and uncertain standard deviations, by using the
Mackey-Glass time series benchmark. A genetic algorithm was used to
optimize the parameters of each of the methods being compared, and the
results show that the intuitionistic fuzzy inference system performs
better than the other methods.
\end{abstract}
